Build Operating Models for SA Species

### 2022-03-16 BuildOM/BuildOMAssess2OM.Rmd
updated rds files

library(bamExtras) # Nikolai's package

@@

@@

@@

```{r build OM VPA2OM, eval=TRUE}
list_Nage_F0_pr_sc <- list() # List for storing values of Nage_F0_pr_sc
vec_to_mat <- function(vec){
  matrix(vec,nrow=dim(naa)[2],ncol=dim(naa)[3],byrow=FALSE,
                    dimnames=dimnames(naa)[2:3])
}

@@

for(rdat_name_i in bam_rdat_sub){
  rdat_i <- standardize_rdat(get(rdat_name_i))
  Name_i <- gsub("rdat_","",rdat_name_i)
  herm_i <- bamStockMisc[Name_i, "herm"]
  OM_name_i <- gsub("rdat","OM",rdat_name_i)
  a.series_i <- rdat_i$a.series
  t.series_i <- rdat_i$t.series

@@

  # NOTE: this will have no effect in ageinitmin_i=0 
  Nage_F0_pr <- expDecay(age=age_i,Z=a.series_i$M,N0=1)                  # Unfished N-at-age per recruit
  Nage_F0_pr_sc <- (Nage_F0_pr/Nage_F0_pr[[paste(ageinitmin_i)]])[["0"]] # Scaling factor for computing unfished numbers at age-0
  R0_i <- R0_i*Nage_F0_pr_sc                                             # Scaled value of R0

@@

          if(!is.null(ObsUser)) {
          if(run_rdat_to_Obs){
            my_rdat <- get(gsub("OM","rdat",OM_name_i))
            ObsUser <- rdat_to_Obs(
                            rdat=my_rdat,
                            Obs=ObsUser,
                            Ind_abb=c("sCT","sTV","sVD"),
                            CAA_abb=c("sCT","sTV","sVD"),
                            CAL_abb=c("sCT","sTV","sVD")
                            )
          }
        }

 OM_i <- VPA2OM(Name=Name_i,
                proyears = proyears,
                interval = interval,
                CurrentYr = CurrentYr_i,
                h=steep_i, R0=R0_i,
                Obs = ObsUser,
                Imp = ImpUser,
                naa=naa, faa=faa, waa=waa, Mataa=Mataa, Maa=Maa, laa=laa,
                nyr_par_mu = 3,
                LowerTri = nyrNoRecDevEnd,
                recind = 0,
                plusgroup = TRUE,
                altinit = 0,
                fixq1 = TRUE,)

@@

>>>>

library(bamExtras) # Nikolai's package
library(bamMSE) # Nikolai's package

@@

# Indicate if operating models should only include indices that were available in the final year of the assessment. logical
AddInd_endyr_only <- TRUE

@@

```{r}
# create completely empty Data object
Data_empty <- local({
  dat <- new("Data")
  for(slotName_i in slotNames(dat)){
    slot_i <- slot(dat,slotName_i)
    if(length(slot_i)>0&is.numeric(slot_i)){
      slot(dat,slotName_i) <- slot_i*NA
    }
  }
  dat
})
```

@@

```{r build OM Assess2OM, eval=TRUE}
list_Nage_F0_pr_sc <- list() # List for storing values of Nage_F0_pr_sc (for plotting hist compared to BAM)
vec_to_mat <- function(vec){
  matrix(vec,nrow=dim(naa)[2],ncol=dim(naa)[3],byrow=FALSE,
                    dimnames=dimnames(naa)[2:3])
}

@@

for(rdat_name_i in bam_rdat_sub){
  rdat_i <- standardize_rdat(get(rdat_name_i))
  Name_i <- gsub("rdat_","",rdat_name_i)
  DataName_i <- gsub("rdat_","Data_",rdat_name_i)
  Data_i <- get(DataName_i)
  Obs_i <- rdat_to_Obs(rdat_i)

  herm_i <- bamStockMisc[Name_i, "herm"]
  OM_name_i <- gsub("rdat","OM",rdat_name_i)
  a.series_i <- rdat_i$a.series
  t.series_i <- rdat_i$t.series

@@

  # NOTE: this will have no effect in ageinitmin_i=0 
  Nage_F0_pr <- exp_decay(age=age_i,Z=a.series_i$M,N0=1)                  # Unfished N-at-age per recruit
  Nage_F0_pr_sc <- (Nage_F0_pr/Nage_F0_pr[[paste(ageinitmin_i)]])[["0"]] # Scaling factor for computing unfished numbers at age-0
  R0_i <- R0_i*Nage_F0_pr_sc                                             # Scaled value of R0

@@

          if(!is.null(ObsUser)) {
          if(run_rdat_to_Obs){
            my_rdat <- get(gsub("OM","rdat",OM_name_i))
            ObsUser <- rdat_to_Obs(
                            rdat=my_rdat,
                            Obs=ObsUser,
                            Ind_abb=c("sTV", "sCT", "sVD", "sBL", "sVL", "sBT", "sFT"),
                            CAA_abb=c("sTV", "sCT", "sVD", "sBL", "sVL", "sBT", "sFT"),
                            CAL_abb=c("sTV", "sCT", "sVD", "sBL", "sVL", "sBT", "sFT")
                            )
          }
        }

 OM_i <- Assess2OM(Name=Name_i,
                proyears = proyears,
                interval = interval,
                CurrentYr = CurrentYr_i,
                h=steep_i, R0=R0_i,
                Obs = ObsUser,
                Imp = ImpUser,
                naa=naa, faa=faa, waa=waa, Mataa=Mataa, Maa=Maa, laa=laa,
                nyr_par_mu = 3,
                LowerTri = nyrNoRecDevEnd,
                recind = 0,
                plusgroup = TRUE,
                altinit = 0,
                fixq1 = TRUE,)

@@

 # Add indices observed in the assessment, their CVs, and their selectivities
 AddInd <- slot(Data_i,"AddInd")
 CV_AddInd <- slot(Data_i,"CV_AddInd")
 AddIndV <- slot(Data_i,"AddIndV")
 AddIndType <- slot(Data_i,"AddIndType")
 AddIunits <- slot(Data_i,"AddIunits")

 if(AddInd_endyr_only){
   # Identify which indices are available (not NA) in the terminal year of the assessment
   AddInd_endyr_ix <- which(!is.na(AddInd[1,,dim(AddInd)[3]])) # Just uses the first sim!!
   AddInd <- AddInd[,AddInd_endyr_ix,,drop=FALSE]
   CV_AddInd <- CV_AddInd[,AddInd_endyr_ix,,drop=FALSE]
   AddIndV <- AddIndV[,AddInd_endyr_ix,,drop=FALSE]
   AddIndType <- AddIndType[AddInd_endyr_ix]
   AddIunits <- AddIunits[AddInd_endyr_ix]
 }

 Data2_i <- Data_empty
 slot(Data2_i,"AddInd") <- AddInd
 slot(Data2_i,"CV_AddInd") <- CV_AddInd
 slot(Data2_i,"AddIndV") <- AddIndV
 slot(Data2_i,"AddIndType") <- AddIndType
 slot(Data2_i,"AddIunits") <- AddIunits

 OM_i@cpars$Data <- Data2_i
